---
title: "kowr"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{kowr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
img {
  display: block;
  margin-left: auto;
  margin-right: auto;
  width: 50%;
}

figcaption {
  text-align: center;
}
</style>

```{r, echo = FALSE}
embed_png <- function(path, dpi = NULL) {
  meta <- attr(png::readPNG(path, native = TRUE, info = TRUE), "info")
  if (!is.null(dpi)) meta$dpi <- rep(dpi, 2)
  knitr::asis_output(paste0(
    "<img src='", path, "'",
    " width=", 400,
    " height=", 300,
    " />"
  ))
}
knitr::opts_chunk$set(comment = "#>", collapse = TRUE)
library(tibble)
```

## Function Examples

### Load the Package

```{r}
library(kowr)
```

<hr>

### back_to_forward()

Primarily for Windows users. When copying file paths in Windows it will use a backslash to separate files, this will throw an error in R. The process of manually changing the backslashes to forward slashes can get highly repetitive. The `back_to_forward()` function will take what is in the user's clipboard and paste the path with the wanted forward slashes. There are two approaches to this.

Example file path saved in clipboard: `C:\Documents\Newsletters\Summer2018.csv`

#### Option 1) Run `back_to_forward()` in the Console

Run `back_to_forward()` in the console. This will output a string with forward slashes.

#### Option 2) Attatch `back_to_forward()` to a Hotkey

`back_to_forward()` is also an add-in called `Back to Forward Slash`. In RStudio near the top click `Addins` and you will see the `kowr` package with the add-in. If you click this add-in it will paste the file path wherever your cursor is located within RStudio. This is not the most ideal way to use this. Since backward_to_forward() is an add-in we can assign the add-in `Back to Forward Slash` to a hotkey.

1. Go to `Tools > Modify Keyboard Shortcuts...` in RStudio
2. Sort by *Name* and find `Back to Forward Slash`
3. Assign a hotkey to it, on my Mac I used `CMD + /`
4. Test out the hotkey with the path in your clipboard!

#### Arguments

- `render`: A Logical. Defaults to `TRUE`. Exists primarily for the sake of internal testing.
- `text`: A String. Default uses the text in your clipboard. This should not be altered from the default. Exists primarily for the sake of internal testing.

<hr>

### clear_plotly_options()

##### Default `plot_ly()` output:

``` r
library(plotly)

p <- plot_ly(data = mtcars, x = ~mpg, y = ~hp, type = "scatter", mode = "markers")

p
```

```{r, echo = FALSE}
embed_png("plotly_with_options.png")
```

##### Remove all buttons on top of the plot:

``` r
p %>% 
  clear_plotly_options()
```

```{r, echo = FALSE}
embed_png("plotly_no_options.png")
```

##### Keep "Zoom in" and "Zoom out" buttons:

``` r
p %>%
  clear_plotly_options(buttons_to_keep = c("zoomIn2d", "zoomOut2d"))
```

```{r, echo = FALSE}
embed_png("plotly_zoom_options.png")
```

#### Arguments:

- `plotly_object` A plotly object.
- `buttons_to_keep` A string. Default is `NULL`. Use a vector of strings for multiple buttons to keep. Below is a list of items with the plotly code that corresponds to the text displayed on the plotly plot when hovering over the buttons.
  - `toImage`: Download plot as a png
  - `zoom2d`: Zoom
  - `pan2d`: Pan
  - `select2d`: Box Select
  - `lasso2d`: Lasso Select
  - `zoomIn2d`: Zoom in
  - `zoomOut2d`: Zoom out
  - `autoScale2d`: Autoscale
  - `resetScale2d`: Reset axes
  - `toggleSpikelines`: Toggle Spike Lines
  - `hoverClosestCartesian`: Show closest data on hover
  - `hoverCompareCartesian`: Compare data on hover
- `keep_logo` A logical. Default is `FALSE`. Set to `TRUE` to keep the "Produced with Plotly" button located in the top right of the plot.

<hr>

### round_up()

Round whole numbers up. This function will always round up to the number place second to the left:

```{r}
round_up(x = 123456)
```

Numbers with only 2 numeric places (tens), then it will round on the tens position value:

```{r}
round_up(x = 19)
```

If needed, we can change the value to a dollar amount. Using `as_dollar = TRUE` will change the numeric value to a character:

```{r}
round_up(x = 1991, format = "dollar")
```

#### Arguments

- `x` A numeric value.
- `format` A boolean. Takes three different options to round up and stylize:
  - `normal`: The default, return the number with no formatting.
  - `dollar`: Return the number with a leading dollar sign along with commas.
  - `comma`: Return the number with commas.

<hr>

### snake_to()

This is useful for when the user wants to use the columns in a presentation such as reports, plots, or dashboards.

I find myself using `stringr::str_to_title()` for a clean way of presenting columns in documents and dashboards. This is the reason the default argument for `snake_to()`'s output is "title". This will only work with snake case (my preferred naming syntax). If you use `snake_to()` on camelCase then it will capitalize it as if it was one word.

```{r}
dat <- tibble(
  this_will_get_cleaned    = c(1, 2, 3),
  thisWillNot    = c("a", "b", "c"),
  cleans_snake_only = c("q", "w", "e"),
  notCamcel = c(10, 12, 14)
)

dat %>%
  snake_to()
```

##### Sentence case:

```{r}
dat %>%
  snake_to(format = "sentence")
```

##### Title case and keep column names only:

```{r}
dat %>%
  snake_to(names_only = TRUE)
```

##### Title case and capitalize the acronyms

```{r}
acronyms = c("GET")
dat %>% 
  snake_to(acronyms = acronyms)
```

##### ggplot titles:

`snake_to()` will also clean up ggplot *x* and *y* axes. Pipe the saved ggplot object into `snake_to()` and it will clean up snake case titles. If there is a legend the title will be capitalized using `str_to_title()`.

```{r, out.width="25%", fig.align="center"}
library(ggplot2)

p <- dat %>% 
  ggplot(aes(x = thisWillNot, y = this_will_get_cleaned)) +
  geom_col()

p

p %>% snake_to()
```

#### Arguments

- `object` A data.frame, ggplot or character vector. A data.frame will have transformed column names. A ggplot object will have transformed X and Y axes.
- `format` A string. The desired target (default is "title") case with options including:
  - `"title"` produces title case
  - `"lower"` produces lower case
  - `"normal"` do not transform the string
  - `"sentence"` produces sentence case
  - `"upper"` produces upper case
- `acronyms` A Character. Default `NULL`. For when acronyms exist in the column names that need to be capitalized. Pass a character vector for when there is more than one acronym. Upper and/or lower case acronyms in this parameter will be accepted. This will only capitalize the wanted words, words that may contain the acronyms letter will NOT be capitalized.
- `names_only` A Logical. Default `FALSE`. If `TRUE`, `snake_to()` will return a vector of transformed column names.
